\pkg{cubble}: An \proglang{R} Package for Organizing and Wrangling Multivariate Spatio-temporal Data

### 2023-06-29 cubble.Rmd
Minor changes section 2.4

```{r face, echo = FALSE, fig.align="center", out.width = "100%", fig.cap = "An illustration of the function \\code{face\\_temporal()} and \\code{face\\_spatial()}: \\code{face\\_temporal()} converts a spatial cubble into a temporal cubbl to focus on the temporal variables. Conversely, \\code{face\\_spatial()} transforms a temporal cubble into a spatial one to for focus on the spatial variables."}
knitr::include_graphics(here::here("figures/diagram-keynotes/diagram-keynotes.001.png"))
```

@@

Methods applies to the \code{tbl_ts} class can also be applied to the temporal cubble objects, for example, checking whether the data contain temporal gaps:

>>>>

```{r face, echo = FALSE, fig.align="center", out.width = "100%", fig.cap = "An illustration of the functions \\code{face\\_temporal()} and \\code{face\\_spatial()}: \\code{face\\_temporal()} converts a spatial cubble into a temporal cubble to focus on the temporal variables. Conversely, \\code{face\\_spatial()} transforms a temporal cubble into a spatial one to focus on the spatial variables."}
knitr::include_graphics(here::here("figures/diagram-keynotes/diagram-keynotes.001.png"))
```

@@

Methods applied to the \code{tbl_ts} class can also be applied to the temporal cubble objects, for example, checking whether the data contain temporal gaps:

### 2023-06-29 cubble.tex
Minor changes section 2.4

\caption{An illustration of the function \code{face\_temporal()} and \code{face\_spatial()}: \code{face\_temporal()} converts a spatial cubble into a temporal cubbl to focus on the temporal variables. Conversely, \code{face\_spatial()} transforms a temporal cubble into a spatial one to for focus on the spatial variables.}\label{fig:face}
\end{figure}
\end{CodeChunk}

>>>>

\caption{An illustration of the functions \code{face\_temporal()} and \code{face\_spatial()}: \code{face\_temporal()} converts a spatial cubble into a temporal cubble to focus on the temporal variables. Conversely, \code{face\_spatial()} transforms a temporal cubble into a spatial one to focus on the spatial variables.}\label{fig:face}
\end{figure}
\end{CodeChunk}
